---
title: "Linear Programming"
author: "Arijit Ray"
date: "April 30, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
###Problem:


A car company produces 2 models, model A and model B. Long-term projections indicate an expected demand of at least 100 model A cars and 80 model B cars each day. Because of limitations on production capacity, no more than 200 model A cars and 170 model B cars can be made daily. To satisfy a shipping contract, a total of at least 200 cars much be shipped each day. If each model A car sold results in a $2000 loss, but each model B car produces a $5000 profit, how many of each type should be made daily to maximize net profits?

**Answer:** So We need to first build the objective function.
Let model B and A be x and y respectively

Therefore, the objective function is z=5000x-2000y ehich we have to maximize to find the profits

Now we have to derive the constraint. From the Problem it is evident that:

x+y=100
x>=80
y>=100

Now lets calculate the values of x and y to maximize the objective function z in R
```{r}
library(lpSolve) #Loading lpSolve library


obj.fun=c(5000,-2000) #Loading the objective function in obj.fun

constr=matrix(c(1,1,1,0,0,1),ncol = 2, byrow = TRUE) #Loading the constraints
constr.dir=c("=",">=",">=")
constr.rhs=c(200,80,100)

mod=lp("max",obj.fun,constr,constr.dir,constr.rhs,compute.sens = TRUE) #Using lp() to solve our problem

mod$solution #Displaying the values of x and y
```
Therefore we have our solution as x=100 and y=100. In order to gain maximum profits, the car company has to sell 100 cars of model A (y) and 100 cars of model B (x). 

Now lets calculate the profits
```{r}
x=100
y=100
z = (5000*x)-(2000*y) #Puting the values of x and y in the objective function

options("scipen"=100, "digits"=4)
cat("Net profit =", z) #Displaying the maximum profit
```
So Maximum Profit is 300000.